Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-20 methodology.tex
some more text about method dispatch

Draft

@@

We now give an example of using dynamic dispatch to model the network engine of the extent manager in the Azure Storage vNext case study.

>>>>

Draft.

@@

We now give an example of using dynamic dispatch to model the network engine of an extent manager in the Azure Storage vNext case study. The network engine is responsible for sending to and receiving messages from the various components of the system. During real execution, the network engine uses a custom remote procedure call (RPC) .NET library for communication. For testing, though, it is desirable to replace all calls to this RPC library with \psharp send and receive operations, which can be captured and systematically interleaved to find bugs. We easily achieved this by exposing the original send message operation of the network engine as a virtual method, and then overriding it for testing. In the overridden method, we created a \psharp event and then we wrapped the original message in this event's payload. Then, instead of invoking the RPC library, we invoke the \texttt{PSharpRuntime.Send(...)} method, which asynchronously sends the event (containing the original message) to the target extent node machine.

For mocking the receive operation, we take advantage of the implicit receive of events in \psharp machines. When a extent node machine receives an event, an appropriate event handler is invoked, which extracts the original message from the payload and then handles it accordingly.

\subsection{Extensibility of the \psharp framework}
\label{sec:method:extend}

Async/Await

custom schedulers, etc

Logs/traces -> user can extend them?
